---
title: 'Question 1 Answer: Movies'
author: '20903936'
date: "24/05/2021"
output:
  pdf_document: default
  html_document: github_document
---


```{r echo=FALSE, eval=FALSE}

# clear all variables in current environment
#rm(list=ls())  

# clear all plots
#graphics.off() 

gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.

# Source in all your functions:
# walk is the 'silent' version of map, which is similar to lapply.
list.files('/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 1/Data Science/20903936 Practical Test/20903936-Practical-Test-2021/Question 1/code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```


#Introduction

This report will aim to test three theories which were discussed around a braai. The theories were based on a discussion regarding claims that movie critics. Specifically, the assertion was that movie critics are near perfect predictors of films' popularity and profitability among audiences. This informal letter will briefly show whether this is not true or not by address theories our dear friend made. 

#The Data 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())  # clear all variables in current environment
graphics.off() # clear all plots

#Loading library to import the data

library(fmxdat)
library(readr)
library(dplyr)
library(tidyverse)
library(data.table)
library(formattable)

#importing the data
my_data <- read.csv("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 1/Data Science/20903936 Practical Test/20903936-Practical-Test-2021/Question 1/data/Movies.csv")

#Checking the characteristics of my data to ensure that variables are well specified.
class(my_data)

summary(my_data)

```

The data seems to fine. Variables have their correct specifications. As can be noted, there are 8 variables and 74 observations.
```{r}

glimpse(my_data)
```

#Theory 1

The first theory that our friend suggested was that she firmly remembers that Rotten Tomatoes was always a great review platform. And if a movie had a rating of more than 80% on Rotten Tomatoes, audiences would rate it above 85% every time.

```{r  echo=FALSE}

#Renaming the vairables 

my_data <- my_data %>% rename(Audience.Score = Audience..score.., Rotten.Tomatoes = Rotten.Tomatoes..)

above_80 <- my_data %>% filter(Rotten.Tomatoes > 80) %>% select(Film,Audience.Score,Rotten.Tomatoes)

print(above_80)
```
As can be seen above, where the Rotten Tomatoes had an above 80 rating, the Audience ratings were not above 85% all the time. 

#Theory 2 

Our dear friend further suggested that Disney Flims may not have had the highest grossing numbers,however they've always been the most profitable of all the leading studios.

```{r  echo=FALSE}

#barplot_movies(data=my_data,fill=Lead.Studio,y=Profitability,x=Lead.Studio,title="Profitability of Films of Each Studio",xlab="Lead.Studio",ylab="Profitability")

g <- ggplot(my_data, aes(fill=Lead.Studio, y=Profitability, x=Lead.Studio)) + 
    geom_bar(position="dodge", stat="identity") +
    ggtitle("Profitability of Films of Each Studio") +
    theme_classic() +
    ylab ("Profitability")+
    xlab("Lead.Studio")

g
```

#Theory 3

The third assertion  made by our dear friend is that audiences are always drawn to the highest grossing Films. In fact she says claims that "the correlation between the world wide grossing numbers and audience scores would be near 80%."

```{r  echo=FALSE}

#if(!require(devtools)) install.packages("devtools")
#library("devtools")

my_data <- my_data %>% rename(Audience.Score = Audience..score.., Rotten.Tomatoes = Rotten.Tomatoes..)

cor(my_data$Worldwide.Gross, my_data$Audience.Score)


```

#Conclusion

It is clear that our friend is misguided. That data clearly shows that her theory ascertions are not ture. 

