---
title: 'Question 1 Answer: Movies'
author: '20903936'
date: "24/05/2021"
output:
  pdf_document: default
  html_document: github_document
---


```{r echo=FALSE, eval=FALSE}

# clear all variables in current environment
#rm(list=ls())  

# clear all plots
#graphics.off() 

gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.

# Source in all your functions:
# walk is the 'silent' version of map, which is similar to lapply.
list.files('/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 1/Data Science/20903936 Practical Test/20903936-Practical-Test-2021/Question 1/code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```


#Introduction

This report will aim to test three theories which were discussed around a braai. The theories were based on a discussion regarding claims that movie critics. Specifically, the assertion was that movie critics are near perfect predictors of films' popularity and profitability among audiences. This informal letter will briefly show whether this is not true or not by address theories our dear friend made. 

#The Data 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())  # clear all variables in current environment
graphics.off() # clear all plots

#Loading library to import the data

library(fmxdat)
library(readr)
library(dplyr)
library(tidyverse)
library(data.table)
library(formattable)

#importing the data
my_data <- read.csv("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 1/Data Science/20903936 Practical Test/20903936-Practical-Test-2021/Question 1/data/Movies.csv")

#Checking the characteristics of my data to ensure that variables are well specified.
class(my_data)

summary(my_data)

```

The data seems to fine. Variables have their correct specifications. As can be noted, there are 8 variables and 74 observations.
```{r}

glimpse(my_data)
```

#Theory 1

The first theory that our friend suggested was that she firmly remembers that Rotten Tomatoes was always a great review platform. And if a movie had a rating of more than 80% on Rotten Tomatoes, audiences would rate it above 85% every time.

```{r  echo=FALSE}

#Renaming the vairables 

my_data <- my_data %>% rename(Audience.Score = Audience..score.., Rotten.Tomatoes = Rotten.Tomatoes..)

above_80 <- my_data %>% filter(Rotten.Tomatoes > 80) %>% select(Film,Audience.Score,Rotten.Tomatoes)

print(above_80)
```

#Theory 2 

```{r  echo=FALSE}


```

#Theory 3

```{r  echo=FALSE}


```

#Conclusion



